Centers and centralizers of higher enveloping algebras of Lie algebras

### 2020-11-02 draft.tex
eugene

Following the proof of this proposition, our main thrust is to interpret this result by exhibiting a topological field theory on the $(n+1)$-dimensional manifold with boundary $M \times \RR_{\geq 0}$ whose factorization algebra of classical observables is equivalent to the constructible factorization algebra $\bC_n(\fg)$. 
\brian{improve this pointer}
\owen{Somewhere please mention that the slogan ``quantization commutes with pushforward'' holds for this class of theories.}

@@

Let $j : \RR_{>0} \hookrightarrow \RR_{\geq 0}$ be the embedding of the open ray into the closed ray. 
Let $\Tilde{\Omega}^\bu (\RR_{\geq 0})$ be the two-term complex
\[
\Omega^0(\RR_{\geq 0}) \xto{j^* \circ \d_{\rm dR}} \Omega^1(\RR_{>0})[-1]  .
\]
The dg commutative algebra structure on $\Tilde{\Omega}^\bu (\RR_{\geq 0})$ is defined by the formula
\[
f \cdot (g \, \d t) = (j^* f) g\, \d t .
\]

Next, let $\Tilde{\Omega}^{\bu}_{c}(\RR_{\geq 0}) \subset \Omega^{\bu}_{c}(\RR_{\geq 0})$ be the sub dg algebra of compactly supported de Rham forms defined by
\[
\Tilde{\Omega}^{\bu}_{c}(\RR_{\geq 0}) = \{\alpha_{0} + \alpha_{1} \d t \; | \; \alpha_{0} (t = 0) = 0 \} .
\]

@@

@@

\end{document}
We call $\ev_f$ the 
$g: Sym(\fg \otimes \Omega (U_J) [1]) \longrightarrow B(U_J) $
let $f\otimes X  $ be an 
element in $\cliels\big(\fg \otimes \Omega^\bu , B\big) \otimes \cliels\big(\fg \otimes \Omega_c^\bu \big)$.  
Let

>>>>

Following the proof of this proposition, our main thrust is to interpret this result by exhibiting a topological field theory on the $(n+1)$-dimensional manifold with boundary $M \times \RR_{\geq 0}$ whose factorization algebra of {\em classical} observables is equivalent to the constructible factorization algebra $\bC_n(\fg)$.
In this sense, the pair $(\bZ_n(\fg), \bU_n(\fg))$ is a model for the quantization of a particular topological field theory on a manifold with boundary.

\owen{Somewhere please mention that the slogan ``quantization commutes with pushforward'' holds for this class of theories.}
\brian{not sure where you wanted to address this request.}

@@

Let $\Tilde{\Omega}^\bu (\RR_{\geq 0})$ be the two-term complex
\[
\{f \in  C^{\infty}(\RR_{\geq 0}) \; | \; f(0) = 0\}  \xto{\d_{\rm dR}} \Omega^1(\RR_{\geq 0})[-1]  .
\]
Notice that this is a subcomplex of the full de Rham complex on $\RR_{\geq 0}$.
In fact, this is a de Rham model for the relative cohomology of the pair $(\RR_{\geq 0}, \partial \RR_{\geq 0} = \{t = 0\})$.

Similarly, let $\Tilde{\Omega}^{\bu}_{c}(\RR_{\geq 0}) \subset \Omega^{\bu}_{c}(\RR_{\geq 0})$ be the subcomplex of compactly supported de Rham forms on $\RR_{\geq 0}$ whose zero form component vanishes at $t = 0$.

Notice that $\Tilde{\Omega}_c^\bu(\RR_{\geq 0})$ (and $\Tilde{\Omega}^\bu_c(\RR_{\geq 0})$) admits the obvious enhancement to a sheaf (cosheaf) of commutative dg algebras on $\RR_{\geq 0}$.

@@

By Proposition \ref{prp:pair}, the constructible factorization algebra $\bC_n(\fg)$ is the classical limit of the factorization sc-pair $(\bZ_n(\fg), \bU_n(\fg))$.
Thus, we have shown that the pair $(\bZ_n(\fg), \bU_n(\fg))$ is
a model for the quantum factorization algebra of observables of topological BF theory on $M \times \RR_{\geq 0}$.

In the ordinary Batalin--Vilkovisky formalism on manifolds without boundary it is the central theme of \cite{CG2} that to any effective family of functionals satisfying the ``quantum master equation'' one can associate a factorization algebra of quantum observables.
On manifolds with boundary, this approach appears in the work of Rabinovich \cite{EugeneNew}.
We expect that one can exhibit our constructible factorization algebra as the quantum factorization algebra of observables associated to a Batalin--Vilkovisky quantization of BF theory on $M \times \RR_{\geq 0}$.

@@

\end{document}

We call $\ev_f$ the 
$g: Sym(\fg \otimes \Omega (U_J) [1]) \longrightarrow B(U_J) $
let $f\otimes X  $ be an 
element in $\cliels\big(\fg \otimes \Omega^\bu , B\big) \otimes \cliels\big(\fg \otimes \Omega_c^\bu \big)$.  
Let
